---
title: "Homework 05"
author: "Greta Savitsky"
date: "2/16/2022"
output: html_document
---
# Question 1

### random integer between 3 and 10
```{r}
n_dims <- as.integer(runif(1, 3, 10))

print(n_dims)
```
### create a vector with n_dims dimensions
```{r}
vector1 <- (1:n_dims**2)
```
### randomize
```{r}
vector1_rand <- sample(vector1)
```
### create matrix
```{r}
m <- matrix(data=vector1_rand,nrow=n_dims)

print(m)
```
### transpose matrix
```{r}
t_m <- t(m)

print(t_m)
```
### sum and mean of first and last rows
```{r}
sum(t_m[1,])

sum(t_m[n_dims,])

mean(t_m[1,])

mean(t_m[n_dims,])
```

### Eigen values
```{r}
e_m <- eigen(t_m, only.values = FALSE, EISPACK = FALSE)

print(e_m)

typeof(e_m$values)

typeof(e_m$vectors)
```
# Question 2

### create 4x4 matrix of random uniform values
```{r}
my_matrix <- (runif(16))

my_matrix <- matrix(data=my_matrix, nrow=4)
```

### create 100-element boolean vector
```{r}
my_logical <- (runif(100))

my_logical <- my_logical > 0.5
```
### create vector of randomized lower-case letters
```{r}
my_letters <- letters[1:26]

my_letters <- sample(my_letters)
```
### create a list with second element of all dfs
```{r}
my_list <- list(my_matrix[2,2], my_logical[2], my_letters[2])
```

### find type of elements
```{r}
typeof(my_matrix[2,2])

typeof(my_logical[2])

typeof(my_letters[2])
```
### find type of dataframe
```{r}
my_vector2 <- c(my_matrix[2,2], my_logical[2], my_letters[2])
typeof(my_vector2)
```
#### my_vector2 is a character vector

# Question 3

### create new dataframe with 26 random units and letters
```{r}
my_units <- runif(26, 0, 10)

my_letters <- LETTERS[1:26]

my_letters <- sample(my_letters)

my_data_frame <- data.frame(my_units,my_letters,stringsAsFactors=FALSE)
```
### sample four random rows and replace numerical values with NAs
```{r}
my_data_frame[sample(nrow(my_data_frame), 4), 1] <- NA
```
### find NA values
```{r}
which(is.na(my_data_frame$my_units))
```
### sort my_letters by alphibetical order
```{r}
my_data_frame[order(my_data_frame$my_letters), ]

my_data_frame
```

### get rid of NAs and find mean of my_units
```{r}
df_clean <- my_data_frame$my_units[!is.na(my_data_frame$my_units)]

mean(df_clean)
```

