---
title: "Homework_10"
author: "Greta Savitsky"
date: "3/30/2022"
output: html_document
---

# 1.
## set up numeric vector and counter
```{r}
counter <- 0
vector <- as.integer(runif(100, max=5, min=-5))
```
## function to count zeros in numeric vector
```{r}
count_zeros <- function(x) {
  for (i in 1:length(x)) {
    if (x[i] == 0) {
      counter <- counter + 1}
  }
  return(counter)
}
```
## run code
```{r}
count_zeros(x=vector)
```

# 2.
## subsetting instead of loop
```{r}
counter <- length(which(vector==0))
print(counter)


```

# 3. 
## creating a specified matrix

################################
# FUNCTION: create_matrix
### purpose: create matrix with x*y dimensions in which each element is the product of the row number x the column number y
### input: x, y
### output:  matrix

```{r}
create_matrix <- function(x,y) {
  mat <- matrix(sample(1:10, size = x*y),
              nrow=x,
              ncol=y)
  for(i in 1:x) {
    for(j in 1:y) {
      (mat[i,j] <- i*j)
    }
  }
  return(mat)
}

create_matrix(2,2)
```

# 4.
## a.
```{r}
group1 <- data.frame(rnorm(50, mean=7, sd=1))
colnames(group1) <- "group1"
head(group1)

group2 <- data.frame(rnorm(50, mean=17, sd=1))
colnames(group2) <- "group2"
head(group2)

group3 <- data.frame(rnorm(50, mean=27, sd=1))
colnames(group3) <- "group3"
head(group3)

library(tidyr)
library(dplyr)

BindGroups <- cbind(group1, group2, group3)
head(BindGroups)

BindGroups <- pivot_longer(BindGroups, cols=group1:group3, names_to = "group")
head(BindGroups)
```
## b.
# FUNCTION: shuffle_and_mean
### purpose: shuffle values in dataframe and return means of each group
### input: dataframe with groups and values
### output: dataframe of means of shuffled groups
```{r}
shuffle_and_mean <- function(x) {
  Shuffle <- transform(x, shuffled=sample(value))
  group1 <- mean(Shuffle$shuffled[Shuffle$group=="group1"])
  group2 <- mean(Shuffle$shuffled[Shuffle$group=="group2"])
  group3 <- mean(Shuffle$shuffled[Shuffle$group=="group3"])
  means <- cbind(group1,group2,group3)
  return(means)
}

shuffle_and_mean(BindGroups)

```
## c.
```{r}

df <- data.frame()
replicate <- c(1:100)

for(i in 1:100) {
  means <- shuffle_and_mean(BindGroups)
  df <- rbind(df,means)
}

df <- cbind(replicate, df)

head(df)
```
## d.
```{r}

library(ggplot2)
library(ggpubr)

p1<-ggplot(df, aes(x=group1)) + 
  geom_histogram(color="black", fill="white")

p2<-ggplot(df, aes(x=group2)) + 
  geom_histogram(color="black", fill="white")

p3<-ggplot(df, aes(x=group3)) + 
  geom_histogram(color="black", fill="white")

all_graphs <- ggarrange(p1, p2, p3,
                        nrow = 1, ncol = 3)

all_graphs
```
```{r}
get_metric <- function(z=NULL) {
                if(is.null(z)){
                  x_obs <- 1:20
                  y_obs <-  x_obs + 10*rnorm(20)
                  z <- data.frame(x_obs,y_obs)} # set up data frame                 
. <- lm(z[,2]~z[,1])
. <- summary(.)
. <- .$coefficients[2,1]

slope <- .
return(slope)
}
```
```{r}
read_data <- function(z=NULL) {
  
                if(is.null(z)){
                  x_obs <- 1:20
                  y_obs <- x_obs + 10*rnorm(20)
                  df <- data.frame(x_obs,
                                   y_obs)} else { 
# set up data frame                 
                  df <-read.table(file=z,
                                   header=TRUE,
                                   sep=",")}

return(df)
}
```
```{r}
get_pval <- function(z=NULL) {
                    if(is.null(z)){
                      z <- list(x_obs=runif(1000),x_sim=runif(1000))}
                      p_lower <- mean(z[[2]]<=z[[1]])
                      p_upper <- mean(z[[2]]>=z[[1]])
return(c(pl=p_lower,pu=p_upper))
}
```

## extra p-value histogram
```{r}
trt_group <- c(rep("Control",4),
                rep("Treatment",5))
print(trt_group)

# create response var
z <- c(runif(4) + 1, runif(5) + 10)
print(z)

# combine into data frame
df <- data.frame(trt=trt_group,res=z)
print(df)

# look at means in observed data
obs <- tapply(df$res,df$trt,mean)
print(obs)


df_sim <- df

# randomization

df_sim$res <- sample(df_sim$res)
print(df_sim)

sim <- tapply(df_sim$res,df$trt,mean)
print(sim)

################################
# FUNCTION: read_data
# purpose: read in or generate data set
# input: file name
# output:  3 column data frame of observed data (x,y)
#-------------------- 
read_data <- function(steep=1, z=NULL) {
  
  if(is.null(z)){
    x_obs <- 1:20
    y_obs <- steep*x_obs + 10*rnorm(20)
    df <- data.frame(x_obs,
                     y_obs)} else {
                       df <- read.table(file=z,
                                        header=TRUE,
                                        sep=",")}
  return(df)

}

################################
# FUNCTION: get_metric
# purpose: 
# input: 
# output:  
#-------------------- 
get_metric <- function(z=NULL) {
  if(is.null(z)){
    x_obs <- 1:20
    y_obs <-  x_obs + 10*rnorm(20)
    z <- data.frame(x_obs,y_obs)} # set up data frame                 
  . <- lm(z[,2]~z[,1])
  . <- summary(.)
  . <- .$coefficients[2,1]
  
  slope <- .
  return(slope)
}

##################################################
# function: shuffle_data
# randomize data for regression analysis
# input: 2-column data frame (x_var,y_var)
# output: 2-column data frame (x_var,y_var)
#------------------------------------------------- 
shuffle_data <- function(z=NULL) {
  if(is.null(z)){
    x_obs <- 1:20
    y_obs <- x_obs + 3*rnorm(20)
    z <- data.frame(x_obs,y_obs)} # set up data frame                 
  z[,2] <- sample(z[,2]) # use sample function with defaults to reshuffle column
  
  return(z)
}

##################################################
# function: get_pval
# calculate p value from simulation
# input: list of observed metric, and vector of simulated metrics
# output: lower, upper tail probability values
#------------------------------------------------- 
get_pval <- function(z=NULL) {
  if(is.null(z)){
    z <- list(x_obs=runif(1),x_sim=runif(1000))}
  p_lower <- mean(z[[2]]<=z[[1]])
  p_upper <- mean(z[[2]]>=z[[1]])
  return(c(pl=p_lower,pu=p_upper))
}

##################################################
# function: plot_ran_test
# create ggplot of histogram of simulated values
# input: list of observed metric and vector of simulated metrics
# output: saved ggplot graph
#------------------------------------------------- 
plot_ran_test <- function(z=NULL) {
  if(is.null(z)){
    z <- list(rnorm(1),rnorm(1000)) }
  df <- data.frame(ID=seq_along(z[[2]]),sim_x=z[[2]])
  
  p1 <- ggplot(data=df) + 
    aes(x=sim_x)
  
  p1 + geom_histogram(aes(fill=I("goldenrod"),
                          color=I("black"))) +
    geom_vline(aes(xintercept=z[[1]],
                   col="blue")) 
  
}
library(ggplot2)
# global variables
n_sim <- 1000
x_sim <- rep(NA,n_sim)
# 
df <- read_data(steep=2)
x_obs <- get_metric(df)

for (i in seq_len(n_sim)) {
  x_sim[i] <- get_metric(shuffle_data(df))
}

slopes <- list(x_obs,x_sim)
get_pval(slopes)
plot_ran_test(slopes)
```