---
title: "Homework_08"
author: "Greta Savitsky"
date: "3/16/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

install.packages("boot")
library(boot)

## Means and SDs from actual data
```{r}
# sd(wit$White.Oak) = 0.1629188
# mean(wit$White.Oak) = 0.1364748
# sd(fia$whiteOak) = 0.9191958
# mean(fia$whiteOak) = 0.1752141
```
### Simulating Pre-Colonization data (n=1000)
```{r}
wit <- rnorm(n=2000, mean=0.136, sd=0.163)
wit <- wit[wit >= 0]
wit <- wit[1:1000]
```
### Simulating Post-Colonization data (n=1000)
```{r}
fia <- rnorm(n=3000, mean=0.175, sd=0.919)
fia <- fia[fia >= 0]
fia <- fia[fia <= 1]
fia <- fia[1:1000]
```
```{r}
par(mfrow=c(1,2))
p1 <- hist(wit)
p2 <- hist(fia)
```

### Paired T-test

```{r}
t.test(wit, fia, paired = TRUE, alternative = "two.sided")
```

# *Because the variance is so different between groups, means can be the same and still be significantly different*
### Simulating Pre-Colonization data (n=1000)
```{r}
wit <- rnorm(n=2000, mean=0.136, sd=0.163)
wit <- wit[wit >= 0]
wit <- wit[1:1000]
```
### Simulating Post-Colonization data (n=1000)
```{r}
fia <- rnorm(n=3000, mean=0.136, sd=0.919)
fia <- fia[fia >= 0]
fia <- fia[fia <= 1]
fia <- fia[1:1000]
```
```{r}
par(mfrow=c(1,2))
p1 <- hist(wit)
p2 <- hist(fia)
```

## Paired T-test

```{r}
t.test(wit, fia, paired = TRUE, alternative = "two.sided")
```
# *n=15 was the lowest sample size to still be significant*
### Simulating Pre-Colonization data (n=15)
```{r}
wit <- rnorm(n=2000, mean=0.136, sd=0.163)
wit <- wit[wit >= 0]
wit <- wit[1:15]
```
### Simulating Post-Colonization data (n=15)
```{r}
fia <- rnorm(n=3000, mean=0.175, sd=0.919)
fia <- fia[fia >= 0]
fia <- fia[fia <= 1]
fia <- fia[1:15]
```
```{r}
par(mfrow=c(1,2))
p1 <- hist(wit)
p2 <- hist(fia)
```

## Paired T-test

```{r}
t.test(wit, fia, paired = TRUE, alternative = "two.sided")
```

