---
title: "Homework_09"
author: "Greta Savitsky"
date: "3/23/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


library(boot)
library(tidyverse)

################################
# FUNCTION: sim_wit
# purpose: simulate witness tree data
# input: sample size
# output: wit data set of length 1000
#-------------------- 
```{r}
sim_wit <- function(size=1000) {
  wit <- rnorm(n=2000, mean=0.136, sd=0.163)
  wit <- wit[wit >= 0]
  wit <- wit[1:size]
  return(wit)
}
```

################################
# FUNCTION: sim_fia
# purpose: simulate FIA data
# input: sample size
# output: fia data set of length 1000
#-------------------- 
```{r}
sim_fia <- function(size=1000) {
  fia <- rnorm(n=3000, mean=0.175, sd=0.919)
  fia <- fia[fia >= 0]
  fia <- fia[fia <= 1]
  fia <- fia[1:size]
  return(fia)
}
```

################################
# FUNCTION: plot_sim
# purpose: simulate FIA data
# input: fia and wit
# output: fia data set of length 1000
#-------------------- 
```{r}
plot_sim <- function() {
par(mfrow=c(1,2))
p1 <- hist(wit)
p2 <- hist(fia)
}
```

################################
# FUNCTION: p_t_test
# purpose: paired t test between wit and fia data
# input: fia and wit
# output: p value
#-------------------- 
```{r}
p_t_test <- function() {
  test <- t.test(wit, fia, paired = TRUE, alternative = "two.sided")
    return(test$p.value)
}
```
#################################
# Global variables
#----------------------------------------------
```{r}
size <- 1000
```
#----------------------------------------------

# Program body

```{r}
wit <- sim_wit()
fia <- sim_fia()
plot <- plot_sim()
p_val <- p_t_test()
```

```{r}
print(head(wit))
print(head(fia))
print(p_val)
```

# Changing std of simulated FIA data to same as Witness data

################################
# FUNCTION: sim_wit
# purpose: simulate witness tree data
# input: sample size
# output: wit data set of length 1000
#-------------------- 
```{r}
sim_wit <- function(size=1000) {
  wit <- rnorm(n=2000, mean=0.136, sd=0.163)
  wit <- wit[wit >= 0]
  wit <- wit[1:size]
  return(wit)
}
```

################################
# FUNCTION: sim_fia
# purpose: simulate FIA data
# input: sample size
# output: fia data set of length 1000
#-------------------- 
```{r}
sim_fia <- function(size=1000) {
  fia <- rnorm(n=3000, mean=0.175, sd=0.163)
  fia <- fia[fia >= 0]
  fia <- fia[fia <= 1]
  fia <- fia[1:size]
  return(fia)
}
```

################################
# FUNCTION: plot_sim
# purpose: simulate FIA data
# input: fia and wit
# output: fia data set of length 1000
#-------------------- 
```{r}
plot_sim <- function() {
par(mfrow=c(1,2))
p1 <- hist(wit)
p2 <- hist(fia)
}
```

################################
# FUNCTION: p_t_test
# purpose: paired t test between wit and fia data
# input: fia and wit
# output: p value
#-------------------- 
```{r}
p_t_test <- function() {
  test <- t.test(wit, fia, paired = TRUE, alternative = "two.sided")
    return(test$p.value)
}
```

################################
# FUNCTION: new_df
# purpose: create a new dataframe combining witness and fia data
# input: fia and wit
# output: wit_fia
#-------------------- 
```{r}
new_df <- function() {
  wit_fia <- merge(wit,fia)
    return(wit_fia)
}
```

#################################
# Global variables
#----------------------------------------------
```{r}
size <- 1000
```
#----------------------------------------------

# Program body

```{r}
wit <- sim_wit()
fia <- sim_fia()
plot <- plot_sim()
p_val <- p_t_test()
wit_fia <- new_df()
```

```{r}
print(head(wit))
print(head(fia))
print(head(wit_fia))
print(p_val)
```
# still significantly different, but less so
